---
title: "WASABI HR and Affect"
output:
  html_document: default
  pdf_document: default
editor_options:
  chunk_output_type: console
---

#Set WD
```{r}
setwd("~/Desktop/Manuscripts/WASABI HR and Affect")
```

#Load Packages
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(tidyr)
library(tidylog)
library(ggplot2)
library(dplyr)
library(psych)
library(lubridate)
library(summarytools)
library(styler)
library(readr)
library(janitor)
library(lubridate)

library(lme4) #for estimating multilevel models
library(lmerTest) #for p-values added to lme4 output
library(texreg) #for better outputs
library(effects) #for visualizing multilevel model effects
library(sjstats) #might have to manually add
library(sjPlot) #Print results
library(sjlabelled) #Allows for custom printed results
library(sjmisc)
library(r2mlm)
library(merTools)
library(DHARMa) #model fit for mlm
```

#Import Data
```{r}
data1 <- data.table::fread("~/Desktop/Manuscripts/WASABI HR and Affect/WASABI_1_psyarxiv.csv")
```

#Functions
```{r}
# Simple function for computing ICC from lmer() output. This will tell you how much variance subjects are taking in the model
ICClmer <- function(out) {
 data.frame(VarCorr(out)) %>% 
  dplyr::rename(variance=vcov, sd=sdcor, re=var1) %>%  
  mutate_all(function(x) ifelse(is.na(x), '', x)) %>%
  data.frame %>% 
  knitr::kable(digits=3) %>% 
  kableExtra::kable_styling()
}

# Simple function for showing the fixed effects output from lmer() output
FElmer <- function(out) {
coef(summary(out)) %>% 
  knitr::kable(digits=3) %>% 
  kableExtra::kable_styling()
}

# Simple function for plotting the fixed effects coefficients form an lmer() output
FEplot <- function(out) {
  feEx <- FEsim(out, 1000)
  library(ggplot2)
  ggplot(feEx[feEx$term!= "(Intercept)", ]) + 
    aes(x = term, ymin = median - 1.96 * sd, 
        ymax = median + 1.96 * sd, y = median) + 
    geom_pointrange() + 
    geom_hline(yintercept = 0, size = I(1.1), color = I("red")) + 
    coord_flip() + 
    theme_bw() + labs(title = "Coefficient Plot of Model", 
                      x = "Median Effect Estimate", y = paste(out@call$formula[[2]]))
}

# Simple function for plotting the random effects from lmer() output
REplot <- function(out) {
  plotREsim(REsim(out, n.sim = 1000))  +
  ggtitle('Plot of Random Effects', subtitle = 'Interval Estimates') 
}

```

#Data Cleaning
##Rename Variables to Convert to Long Format
```{r}
data2 <- data1 %>% 
  rename(hr_1 = HR1,
    hr_2 = HR2,
    hr_3 = HR3,
    hr_4 = HR4,
    hr_5 = HR5,
    hr_6 = HR6,
    hr_7 = HR7,
    vasstress_1 = VAS1b,
    vasstress_2 = VAS2b,
    vasstress_3 = VAS3b,
    vasstress_4 = VAS4b,
    vasstress_5 = VAS5b,
    vasstress_6 = VAS6b,
    vasstress_7 = VAS7b,
    vasanxiety_1 = VAS1c,
    vasanxiety_2 = VAS2c,
    vasanxiety_3 = VAS3c,
    vasanxiety_4 = VAS4c,
    vasanxiety_5 = VAS5c,
    vasanxiety_6 = VAS6c,
    vasanxiety_7 = VAS7c) %>% 
  dplyr::select(
    SID,
    Flagged,
    ConditionLabel,
    Gender,
    RaceEthnicity,
    Age,
    hr_1,
    hr_2,
    hr_3,
    hr_4,
    hr_5,
    hr_6,
    hr_7,
    vasstress_1,
    vasstress_2,
    vasstress_3,
    vasstress_4,
    vasstress_5,
    vasstress_6,
    vasstress_7,
    vasanxiety_1,
    vasanxiety_2,
    vasanxiety_3,
    vasanxiety_4,
    vasanxiety_5,
    vasanxiety_6,
    vasanxiety_7,
    BDIScore,
    GAD7Score)

##Remove Flagged Cases
data3 <- data2 %>% 
  dplyr::filter(Flagged != 1) %>% 
  dplyr::select(-Flagged)
```

##Turn Data Into Long
```{r}
data_long1 <- data3 %>%  
  pivot_longer(cols = c(-SID, -ConditionLabel, -Gender, -Age, -RaceEthnicity, -BDIScore, -GAD7Score), names_sep="_(?=[^_]+$)", names_to = c(".value", "wave"))

data_long1 <- data_long1 %>% 
  dplyr::select(SID,
                ConditionLabel,
                Gender,
                RaceEthnicity,
                Age,
                wave,
                BDIScore, GAD7Score,
                hr,
                vasstress,
                vasanxiety)
```

##Visualize Missing Data
```{r}
#Overall missing data
data_long1 %>% 
  naniar::vis_miss()

#Count of missing data
naniar::gg_miss_var(data_long1, wave)
```

##Check Structure
```{r}
str(data_long1)

#Make Variables Factor
data_long1[,1:6] <- lapply(data_long1[,1:6], as.factor)

#Make Variables Numeric
data_long1[,7:11] <- lapply(data_long1[,7:11], as.numeric)
```

##Check Distribution
```{r}
describeBy(data_long1) #skew ok
```

##Check Outliers
```{r}
#Replace biologically implausible heart rate values with NA
boxplot(data_long1$hr)

#data_long1 <- data_long1 %>% 
#  naniar::replace_with_na(replace = list(hr = 0))
```

#Figures
##Plot Variability in NSSI and SI
```{r}
#HR Trajectory by Condition
hr_trajectory <- ggplot(data=subset(data_long1), aes(x = wave, y = hr, color = ConditionLabel)) +
  geom_line(aes(group = SID), alpha = .1) + #This fades the individual lines
  geom_point(position=position_jitter(h=0.05, w=0.05), shape = 21, alpha = 0.5, size = 1) +
  stat_summary(data=subset(data_long1), aes(group=ConditionLabel), fun=mean, geom="smooth") + 
  theme(axis.ticks = element_line(colour = "black"), 
    panel.grid.major = element_line(colour = "white"), 
    panel.grid.minor = element_line(colour = "white"), 
    axis.title = element_text(size = 10), 
    axis.text = element_text(size = 10, colour = "black"), 
    axis.text.x = element_text(colour = "black"), 
    axis.text.y = element_text(colour = "black"), 
    plot.title = element_text(size = 10), 
    legend.text = element_text(size = 10), 
    legend.title = element_text(size = 10), 
    panel.background = element_rect(fill = "white"), 
    legend.key = element_rect(fill = "white"), 
    legend.background = element_rect(fill = "white")) +
  labs(title = "Heart Rate Trajectory by Condition", x = "Time", y = "Heart Rate", colour = "Condition")

hr_trajectory

#Stress Trajectory by Condition
stress_trajectory <- ggplot(data=subset(data_long1), aes(x = wave, y = vasstress, color = ConditionLabel)) +
  geom_line(aes(group = SID), alpha = .1) + #This fades the individual lines
  geom_point(position=position_jitter(h=0.05, w=0.05),
             shape = 21, alpha = 0.5, size = 1) +
  stat_summary(data=subset(data_long1), aes(group=ConditionLabel), fun=mean, geom="smooth") + 
  theme(axis.ticks = element_line(colour = "black"), 
    panel.grid.major = element_line(colour = "white"), 
    panel.grid.minor = element_line(colour = "white"), 
    axis.title = element_text(size = 10), 
    axis.text = element_text(size = 10, colour = "black"), 
    axis.text.x = element_text(colour = "black"), 
    axis.text.y = element_text(colour = "black"), 
    plot.title = element_text(size = 10), 
    legend.text = element_text(size = 10), 
    legend.title = element_text(size = 10), 
    panel.background = element_rect(fill = "white"), 
    legend.key = element_rect(fill = "white"), 
    legend.background = element_rect(fill = "white")) +
  labs(title = "Stress Trajectory by Condition", x = "Time", y = "Stress", colour = "Condition")

stress_trajectory

#Anxiety Trajectory by Condition
anxiety_trajectory <- ggplot(data=subset(data_long1), aes(x = wave, y = vasanxiety, color = ConditionLabel)) +
  geom_line(aes(group = SID), alpha = .1) + #This fades the individual lines
  geom_point(position=position_jitter(h=0.05, w=0.05),
             shape = 21, alpha = 0.5, size = 1) +
  stat_summary(data=subset(data_long1), aes(group=ConditionLabel), fun=mean, geom="smooth") + 
  theme(axis.ticks = element_line(colour = "black"), 
    panel.grid.major = element_line(colour = "white"), 
    panel.grid.minor = element_line(colour = "white"), 
    axis.title = element_text(size = 10), 
    axis.text = element_text(size = 10, colour = "black"), 
    axis.text.x = element_text(colour = "black"), 
    axis.text.y = element_text(colour = "black"), 
    plot.title = element_text(size = 10), 
    legend.text = element_text(size = 10), 
    legend.title = element_text(size = 10), 
    panel.background = element_rect(fill = "white"), 
    legend.key = element_rect(fill = "white"), 
    legend.background = element_rect(fill = "white")) +
  labs(title = "Anxiety Trajectory by Condition", x = "Time", y = "Anxiety", colour = "Condition")

anxiety_trajectory

#Merge Figures
ggpubr::ggarrange(hr_trajectory, stress_trajectory, anxiety_trajectory, 
                  labels = c("A", "B", "C"),
                  ncol = 1, nrow = 3)
```

##Plot
##Heart Rate
```{r}
sumrepdat_hr <- Rmisc::summarySE(data_long1, measurevar = "hr",
                              groupvars=c("ConditionLabel", "wave"))

hr_plot2 <- ggplot(data_long1, aes(x = wave, y = hr, fill = ConditionLabel)) +
  PupillometryR::geom_flat_violin(aes(fill = ConditionLabel), position = position_nudge(x = .2, y = 0), adjust = 1.5, trim = FALSE, alpha = .5, colour = NA) +
  geom_point(aes(x = as.numeric(wave) - .15, y = hr, colour = ConditionLabel), position = position_jitter(width = .05), size = .25, shape = 20) +
  geom_boxplot(aes(x = wave, y = hr, fill = ConditionLabel), outlier.shape = NA, alpha = .5, width = .2, colour = "black") +
  geom_line(data = sumrepdat_hr, aes(x = as.numeric(wave) + .1, y = hr, group = ConditionLabel, colour = ConditionLabel), linetype = 3) +
  geom_point(data = sumrepdat_hr, aes(x = as.numeric(wave) + .1, y = hr, group = ConditionLabel, colour = ConditionLabel), shape = 18) +
  geom_errorbar(data = sumrepdat_hr, aes(x = as.numeric(wave) + .1, y = hr, group = ConditionLabel, colour = ConditionLabel, ymin = hr - se, ymax = hr + se), width = .05) +
  scale_colour_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2") +
  labs(title = "Heart Rate Trajectory by Condition", x = "Time", y = "Heart Rate", colour = "Condition") +
  guides(color=guide_legend("Condition"), fill = FALSE) +
# coord_flip()+
  theme(axis.line = element_line(linetype = "solid"), 
    panel.grid.major = element_line(colour = "white"), 
    panel.grid.minor = element_line(colour = "white"), 
    panel.background = element_rect(fill = "white")) +
  theme(legend.key = element_rect(fill = "white"), 
    legend.background = element_rect(fill = "white"))

hr_plot2
```

###Stress
```{r}
sumrepdat_stress <- Rmisc::summarySE(data_long1, measurevar = "vasstress",
                              groupvars=c("ConditionLabel", "wave"))

stress_plot2 <- ggplot(data_long1, aes(x = wave, y = vasstress, fill = ConditionLabel)) +
  PupillometryR::geom_flat_violin(aes(fill = ConditionLabel), position = position_nudge(x = .2, y = 0), adjust = 1.5, trim = FALSE, alpha = .5, colour = NA) +
  geom_point(aes(x = as.numeric(wave) - .15, y = vasstress, colour = ConditionLabel), position = position_jitter(width = .05), size = .25, shape = 20) +
  geom_boxplot(aes(x = wave, y = vasstress, fill = ConditionLabel), outlier.shape = NA, alpha = .5, width = .2, colour = "black") +
  geom_line(data = sumrepdat_stress, aes(x = as.numeric(wave) + .1, y = vasstress, group = ConditionLabel, colour = ConditionLabel), linetype = 3) +
  geom_point(data = sumrepdat_stress, aes(x = as.numeric(wave) + .1, y = vasstress, group = ConditionLabel, colour = ConditionLabel), shape = 18) +
  geom_errorbar(data = sumrepdat_stress, aes(x = as.numeric(wave) + .1, y = vasstress, group = ConditionLabel, colour = ConditionLabel, ymin = vasstress - se, ymax = vasstress + se), width = .05) +
  scale_colour_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2") +
  labs(title = "Stress Trajectory by Condition", x = "Time", y = "Stress", colour = "Condition") +
  guides(color=guide_legend("Condition"), fill = FALSE) +
# coord_flip()+
  theme(axis.line = element_line(linetype = "solid"), 
    panel.grid.major = element_line(colour = "white"), 
    panel.grid.minor = element_line(colour = "white"), 
    panel.background = element_rect(fill = "white")) +
  theme(legend.key = element_rect(fill = "white"), 
    legend.background = element_rect(fill = "white"))

stress_plot2
```

##Anxiety
```{r}
sumrepdat_anxiety <- Rmisc::summarySE(data_long1, measurevar = "vasanxiety",
                              groupvars=c("ConditionLabel", "wave"))

anxiety_plot2 <- ggplot(data_long1, aes(x = wave, y = vasanxiety, fill = ConditionLabel)) +
  PupillometryR::geom_flat_violin(aes(fill = ConditionLabel), position = position_nudge(x = .2, y = 0), adjust = 1.5, trim = FALSE, alpha = .5, colour = NA) +
  geom_point(aes(x = as.numeric(wave) - .15, y = vasanxiety, colour = ConditionLabel), position = position_jitter(width = .05), size = .25, shape = 20) +
  geom_boxplot(aes(x = wave, y = vasanxiety, fill = ConditionLabel), outlier.shape = NA, alpha = .5, width = .2, colour = "black") +
  geom_line(data = sumrepdat_anxiety, aes(x = as.numeric(wave) + .1, y = vasanxiety, group = ConditionLabel, colour = ConditionLabel), linetype = 3) +
  geom_point(data = sumrepdat_anxiety, aes(x = as.numeric(wave) + .1, y = vasanxiety, group = ConditionLabel, colour = ConditionLabel), shape = 18) +
  geom_errorbar(data = sumrepdat_anxiety, aes(x = as.numeric(wave) + .1, y = vasanxiety, group = ConditionLabel, colour = ConditionLabel, ymin = vasanxiety - se, ymax = vasanxiety + se), width = .05) +
  scale_colour_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2") +
  labs(title = "Anxiety Trajectory by Condition", x = "Time", y = "Anxiety", colour = "Condition") +
  guides(color=guide_legend("Condition"), fill = FALSE) +
# coord_flip()+
  theme(axis.line = element_line(linetype = "solid"), 
    panel.grid.major = element_line(colour = "white"), 
    panel.grid.minor = element_line(colour = "white"), 
    panel.background = element_rect(fill = "white")) +
  theme(legend.key = element_rect(fill = "white"), 
    legend.background = element_rect(fill = "white"))

anxiety_plot2
```

##Figure
```{r}
ggpubr::ggarrange(hr_plot2, stress_plot2, anxiety_plot2, 
                  labels = c("A", "B", "C"),
                  ncol = 1, nrow = 3)
```


#Covariation Figure
##Convert variables to Z-Score
```{r}
data_long2 <- data_long1
data_long2$hr_zscore <- scale(data_long2$hr)
data_long2$stress_zscore <- scale(data_long2$vasstress)
data_long2$anxiety_zscore <- scale(data_long2$vasanxiety)
str(data_long2)
```

#Descriptives

##Participants by Condition
```{r}
data3 %>% 
  freq(ConditionLabel)
```


##Sex
```{r}
freq(data3$Gender)
```


##Turn Data Into Long
```{r}
#Stress Data
hr_stress_data <- data_long2 %>%  
  pivot_longer(cols = c(hr_zscore, stress_zscore), names_to = "variable", values_to = "value")

str(hr_stress_data)
hr_stress_data$variable <- as.factor(hr_stress_data$variable)
hr_stress_data$wave <- as.numeric(hr_stress_data$wave)

#Anxiety Data
hr_anxiety_data <- data_long2 %>%  
  pivot_longer(cols = c(hr_zscore, anxiety_zscore), names_to = "variable", values_to = "value")

str(hr_anxiety_data)
hr_anxiety_data$variable <- as.factor(hr_anxiety_data$variable)
hr_anxiety_data$wave <- as.numeric(hr_anxiety_data$wave)

#Stress and Anxiety Data
hr_stressanxiety_data <- data_long2 %>%  
  pivot_longer(cols = c(hr_zscore, stress_zscore, anxiety_zscore), names_to = "variable", values_to = "value")

str(hr_stressanxiety_data)
hr_stress_data$variable <- as.factor(hr_stress_data$variable)
hr_stress_data$wave <- as.numeric(hr_stress_data$wave)

hr_stressanxiety_data2 <- hr_stressanxiety_data %>% 
  dplyr::select(SID,
                wave,
                value,
                variable)

hr_stressanxiety_data2$variable <- as.factor(hr_stressanxiety_data2$variable)

str(hr_stressanxiety_data2)

hr_stress_data2 <- hr_stress_data %>% 
  group_by(SID) %>% mutate(sample = seq_along(SID))

duplicated <- duplicated(hr_stressanxiety_data[,c("SID", "wave", "variable", "value")])
freq(duplicated)
```

##Graph 1
```{r}
hr_stressanxiety_data2$variable <- plyr::revalue(hr_stressanxiety_data2$variable, c("hr_zscore" = "Heart Rate (Z-Score)"))
hr_stressanxiety_data2$variable <- plyr::revalue(hr_stressanxiety_data2$variable, c("stress_zscore" = "Stress (Z-Score"))
hr_stressanxiety_data2$variable <- plyr::revalue(hr_stressanxiety_data2$variable, c("anxiety_zscore" = "Anxiety (Z-Score"))

#Plot Stress and HR
hr_stressanxiety_graph <- ggplot(data=subset(hr_stressanxiety_data2), aes(x = wave, y = value, color = variable)) +
  #geom_line(aes(group = SID), alpha = .1) + #This fades the individual lines
  geom_line(aes(group = interaction(SID, variable)), alpha = .1) +
  geom_point(position=position_jitter(h=0.05, w=0.05),
             shape = 21, alpha = 0.5, size = 1) +
  stat_summary(data=subset(hr_stressanxiety_data2), aes(group=variable), fun=mean, geom="smooth") + 
  theme(axis.ticks = element_line(colour = "black"), 
    panel.grid.major = element_line(colour = "white"), 
    panel.grid.minor = element_line(colour = "white"), 
    axis.title = element_text(size = 10), 
    axis.text = element_text(size = 10, colour = "black"), 
    axis.text.x = element_text(colour = "black"), 
    axis.text.y = element_text(colour = "black"), 
    plot.title = element_text(size = 10), 
    legend.text = element_text(size = 10), 
    legend.title = element_text(size = 10), 
    panel.background = element_rect(fill = "white"), 
    legend.key = element_rect(fill = "white"), 
    legend.background = element_rect(fill = "white")) +
  labs(title = "Covariation of Heart Rate, Stress, and Anxiety", x = "Wave", y = "Value (Z-Scored)", colour = "Variable")

hr_stressanxiety_graph

#Animate
hr_stressanxiety_graph + gganimate::transition_reveal(as.numeric(wave))

gganimate::anim_save("hr_stressanxiety_covariation.gif")
```

```{r}
#Plot Stress and HR
hr_stress_graph <- ggplot(data=subset(hr_stress_data), aes(x = wave, y = as.numeric(value), color = variable)) +
  #geom_line(aes(group = SID), alpha = .1) + #This fades the individual lines
  geom_line(aes(group = interaction(SID, variable)), alpha = .1) +
  geom_point(position=position_jitter(h=0.05, w=0.05),
             shape = 21, alpha = 0.5, size = 1) +
  stat_summary(data=subset(hr_stress_data), aes(group=variable), fun=mean, geom="smooth") + 
  theme(axis.ticks = element_line(colour = "black"), 
    panel.grid.major = element_line(colour = "white"), 
    panel.grid.minor = element_line(colour = "white"), 
    axis.title = element_text(size = 10), 
    axis.text = element_text(size = 10, colour = "black"), 
    axis.text.x = element_text(colour = "black"), 
    axis.text.y = element_text(colour = "black"), 
    plot.title = element_text(size = 10), 
    legend.text = element_text(size = 10), 
    legend.title = element_text(size = 10), 
    panel.background = element_rect(fill = "white"), 
    legend.key = element_rect(fill = "white"), 
    legend.background = element_rect(fill = "white")) +
  labs(title = "Covariation of Heart Rate and Stress", x = "Wave", y = "Value (Z-Scored)", colour = "Variable")

hr_stress_graph

#Animate
hr_stress_graph + gganimate::transition_reveal(wave)

gganimate::anim_save("hr_stress_covariation.gif")

#Plot Anxiety and HR
hr_anxiety_graph <- ggplot(data=subset(hr_anxiety_data), aes(x = wave, y = value, color = variable)) +
  #geom_line(aes(group = SID), alpha = .1) + #This fades the individual lines
  geom_line(aes(group = interaction(SID, variable)), alpha = .1) +
  geom_point(position=position_jitter(h=0.05, w=0.05), shape = 21, alpha = 0.1, size = 1) +
  stat_summary(data=subset(hr_anxiety_data), aes(group=variable), fun=mean, geom="smooth", size = 2) + 
  theme(axis.ticks = element_line(colour = "black"), 
        panel.grid.major = element_line(colour = "white"), 
        panel.grid.minor = element_line(colour = "white"), 
        axis.title = element_text(size = 10), 
        axis.text = element_text(size = 10, colour = "black"), 
        axis.text.x = element_text(colour = "black"), 
        axis.text.y = element_text(colour = "black"), 
        plot.title = element_text(size = 10), 
        legend.text = element_text(size = 10), 
        legend.title = element_text(size = 10), 
        panel.background = element_rect(fill = "white"), 
        legend.key = element_rect(fill = "white"), 
        legend.background = element_rect(fill = "white")) +
  labs(title = "Covariation of Heart Rate and Anxiety", x = "Wave", y = "Value (Z-Scored)", colour = "Variable")

hr_anxiety_graph

#Animate
hr_anxiety_graph + gganimate::transition_reveal(wave)

gganimate::anim_save("hr_anxiety_covariation.gif")
```

##Difference by Time
```{r}
set.seed(1876)

#HR
ggstatsplot::ggwithinstats(
  data = data_long1,
  x = wave,
  y = hr,
  title = "Heart Rate by Wave",
  xlab = "Wave",
  ylab = "Heart Rate",
  pairwise.comparisons = TRUE
)

#Stress
ggstatsplot::ggwithinstats(
  data = data_long1,
  x = wave,
  y = vasstress,
  title = "Stress by Wave",
  xlab = "Wave",
  ylab = "Stress",
  pairwise.comparisons = TRUE
)

#Anxiety
ggstatsplot::ggwithinstats(
  data = data_long1,
  x = wave,
  y = vasanxiety,
  title = "Anxiety by Wave",
  xlab = "Wave",
  ylab = "Anxiety",
  pairwise.comparisons = TRUE
)
```

#Analyses
##Create Between and Within Person Terms
```{r}
data_long2 <- bmlm::isolate(data_long1, by = "SID",
             value = c("hr", "vasstress", "vasanxiety"),
             which = "both")
```

##Change Condition Reference Level
```{r}
data_long2 <- data_long2 %>% 
  mutate(ConditionLabel = relevel(ConditionLabel, 2))
```

##Winsorize
```{r}
data_long2$hr_win <- DescTools::Winsorize(data_long2$hr, na.rm = TRUE)
data_long2$vasstress_win <- DescTools::Winsorize(data_long2$vasstress, na.rm = TRUE)
data_long2$vasanxiety_win <- DescTools::Winsorize(data_long2$vasanxiety, na.rm = TRUE)
data_long2$GAD7Score_win <- DescTools::Winsorize(data_long2$GAD7Score, na.rm = TRUE)
data_long2$BDIScore_win <- DescTools::Winsorize(data_long2$BDIScore, na.rm = TRUE)
```

##Analysis
###Create Between and Within Person Terms
```{r}
data_long3 <- bmlm::isolate(data_long2, by = "SID",
             value = c("hr_win", "vasstress_win", "vasanxiety_win"),
             which = "both")
```

##Stress Models
###HR Predicting Stress- Model 1 random intercepts and fixed slope
```{r}
hr_stress_model_win1 <- lmer(vasstress_win ~ 1 + hr_win_cb + hr_win_cw + BDIScore_win + GAD7Score_win + ConditionLabel + Gender + (1 | SID), REML = TRUE, data = data_long3)
summary(hr_stress_model_win1)
confint(hr_stress_model_win1)
performance::check_convergence(hr_stress_model_win1) #converged okay
performance::check_singularity(hr_stress_model_win1) #is not singular
performance::r2(hr_stress_model_win1)
performance::icc(hr_stress_model_win1)
ggstatsplot::ggcoefstats(hr_stress_model_win1)
performance::check_model(hr_stress_model_win1)
performance::model_performance(hr_stress_model_win1)
FElmer(hr_stress_model_win1)
FEplot(hr_stress_model_win1)
ICClmer(hr_stress_model_win1)
REplot(hr_stress_model_win1)
```

###HR Predicting Stress- Model 2 random intercepts and random slope
```{r}
hr_stress_model_win2 <- lmer(vasstress_win ~ 1 + hr_win_cb + hr_win_cw + BDIScore_win + GAD7Score_win + ConditionLabel + Gender + (1 + hr_win_cw | SID), REML = TRUE, data = data_long3)
summary(hr_stress_model_win2)
confint(hr_stress_model_win2)
performance::check_convergence(hr_stress_model_win2) #converged okay
performance::check_singularity(hr_stress_model_win2) #is not singular
performance::r2(hr_stress_model_win2)
performance::icc(hr_stress_model_win2)
ggstatsplot::ggcoefstats(hr_stress_model_win2)
performance::check_model(hr_stress_model_win2)
performance::model_performance(hr_stress_model_win2)
FElmer(hr_stress_model_win2)
FEplot(hr_stress_model_win2)
ICClmer(hr_stress_model_win2)
REplot(hr_stress_model_win2)
```

###Compare Models
```{r}
data_long3_compare <- na.omit(data_long3)

hr_stress_model_unconditional_compare <- lmer(vasstress_win ~ 1 + (1| SID), REML = TRUE, data = data_long3_compare)

hr_stress_model1_compare <- lmer(vasstress_win ~ 1 + hr_win_cb + hr_win_cw + BDIScore_win + GAD7Score_win + ConditionLabel + Gender + (1 | SID), REML = TRUE, data = data_long3_compare)

#These two models are equivalent
hr_stress_model2_compare <- lmer(vasstress_win ~ 1 + hr_win_cb + hr_win_cw + BDIScore_win + GAD7Score_win + ConditionLabel + Gender + (1 + hr_win_cw | SID), REML = TRUE, data = data_long3_compare, control = lmerControl(optimizer ="Nelder_Mead"))

#Compare Models
anova(hr_stress_model_unconditional_compare, hr_stress_model1_compare, hr_stress_model2_compare)
```

##Anxiety Models
###HR Predicting Stress- Model 1 random intercepts and fixed slope
```{r}
hr_anxiety_model_win1 <- lmer(vasstress_win ~ 1 + hr_win_cb + hr_win_cw + BDIScore_win + GAD7Score_win + ConditionLabel + Gender + (1 | SID), REML = TRUE, data = data_long3)
summary(hr_anxiety_model_win1)
confint(hr_anxiety_model_win1)
performance::check_convergence(hr_anxiety_model_win1) #converged okay
performance::check_singularity(hr_anxiety_model_win1) #is not singular
performance::r2(hr_anxiety_model_win1)
performance::icc(hr_anxiety_model_win1)
ggstatsplot::ggcoefstats(hr_anxiety_model_win1)
performance::check_model(hr_anxiety_model_win1)
performance::model_performance(hr_anxiety_model_win1)
FElmer(hr_anxiety_model_win1)
FEplot(hr_anxiety_model_win1)
ICClmer(hr_anxiety_model_win1)
REplot(hr_anxiety_model_win1)
```

###HR Predicting Stress- Model 2 random intercepts and random slope
```{r}
hr_anxiety_model_win2 <- lmer(vasstress_win ~ 1 + hr_win_cb + hr_win_cw + BDIScore_win + GAD7Score_win + ConditionLabel + Gender + (1 + hr_win_cw | SID), REML = TRUE, data = data_long3, control = lmerControl(optimizer ="Nelder_Mead"))
summary(hr_anxiety_model_win2)
confint(hr_anxiety_model_win2)
performance::check_convergence(hr_anxiety_model_win2) #converged okay
performance::check_singularity(hr_anxiety_model_win2) #is not singular
performance::r2(hr_anxiety_model_win2)
performance::icc(hr_anxiety_model_win2)
ggstatsplot::ggcoefstats(hr_anxiety_model_win2)
performance::check_model(hr_anxiety_model_win2)
performance::model_performance(hr_anxiety_model_win2)
FElmer(hr_anxiety_model_win2)
FEplot(hr_anxiety_model_win2)
ICClmer(hr_anxiety_model_win2)
REplot(hr_anxiety_model_win2)
```

###Compare Models
```{r}
hr_anxiety_model_unconditional_compare <- lmer(vasanxiety_win ~ 1 + (1| SID), REML = TRUE, data = data_long3_compare)

hr_anxiety_model1_compare <- lmer(vasanxiety_win ~ 1 + hr_win_cb + hr_win_cw + BDIScore_win + GAD7Score_win + ConditionLabel + Gender + (1 | SID), REML = TRUE, data = data_long3_compare)

#These two models are equivalent
hr_anxiety_model2_compare <- lmer(vasanxiety_win ~ 1 + hr_win_cb + hr_win_cw + BDIScore_win + GAD7Score_win + ConditionLabel + Gender + (1 + hr_win_cw | SID), REML = TRUE, data = data_long3_compare, control = lmerControl(optimizer ="Nelder_Mead"))

#Compare Models
anova(hr_anxiety_model_unconditional_compare, hr_anxiety_model1_compare, hr_anxiety_model2_compare)
```

##Create Table
```{r}
tab_model(hr_stress_model_win2, hr_anxiety_model_win2,
          dv.labels = c("Stress Model Winsorized", "Anxiety Model Winsorized"),
          string.ci = "95% CI",
          string.p = "P-Value",
          show.se = TRUE,
          show.std = TRUE,
          string.se = "SE",
          show.fstat = TRUE,
          digits = 3,
          show.aic = TRUE,
          file = "~/Desktop/Manuscripts/WASABI HR and Affect/Tables/Output_Winsorized.doc")
```

##HR Predicting Stress
```{r}
hr_stress_model_unconditional <- lmer(vasstress ~ 1 + hr_cb + hr_cw + (1| SID), REML = TRUE, data = data_long2)

hr_stress_model1 <- lmer(vasstress ~ 1 + hr_cb + hr_cw + BDIScore + GAD7Score + ConditionLabel + Gender + (1 + hr_cw | SID), REML = TRUE, data = data_long2, control = lmerControl(optimizer ="Nelder_Mead"))
summary(hr_stress_model1)
confint(hr_stress_model1)
performance::check_convergence(hr_stress_model1) #converged okay
performance::check_singularity(hr_stress_model1) #is not singular
performance::r2(hr_stress_model1)
performance::icc(hr_stress_model1)
ggstatsplot::ggcoefstats(hr_stress_model1)
performance::check_model(hr_stress_model1)
performance::check_collinearity(hr_stress_model1)
performance::model_performance(hr_stress_model1)
FElmer(hr_stress_model1)
FEplot(hr_stress_model1)
ICClmer(hr_stress_model1)
REplot(hr_stress_model1)
```

##HR Predicting Anxiety
```{r}
hr_anxiety_model_unconditional <- lmer(vasanxiety ~ 1 +  (1 | SID), REML = TRUE, data = data_long2)

hr_anxiety_model1 <- lmer(vasanxiety ~ 1 + hr_cb + hr_cw + BDIScore + GAD7Score + ConditionLabel + Gender + (1 + hr_cw | SID), REML = TRUE, data = data_long2)

summary(hr_anxiety_model1)
confint(hr_anxiety_model1)
performance::check_convergence(hr_anxiety_model1) #converged okay
performance::check_singularity(hr_anxiety_model1) #is not singular
performance::r2(hr_anxiety_model1)
performance::icc(hr_anxiety_model1)
ggstatsplot::ggcoefstats(hr_anxiety_model1)
performance::check_model(hr_anxiety_model1)
performance::model_performance(hr_anxiety_model1)
```

##Create Table
```{r}
tab_model(hr_stress_model1, hr_anxiety_model1,
          dv.labels = c("Stress Model", "Anxiety Model"),
          string.ci = "95% CI",
          string.p = "P-Value",
          show.std = TRUE,
          show.se = TRUE,
          string.se = "SE",
          show.fstat = TRUE,
          digits = 3,
          show.aic = TRUE,
          file = "~/Desktop/Manuscripts/WASABI HR and Affect/Tables/Output.doc")
```

#Sensitivity Analyses


#Association Between BDIScore and GAD7Score with HR
```{r}

```







